COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-05-20 main.tex
Finalize draft

\documentclass[onecolumn]{aastex63}
\usepackage{natbib}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
\bibliographystyle{aasjournal}

@@

\begin{abstract}
In circumstellar disks, collisional grinding of planetesimals produces second-generation dust, which can be observed through thermal 
emission. While it remains unclear when second-generation dust first becomes a major component of the total dust content, the presence of 
such dust and potentially the substructure within it can be used to explore a disk's physical conditions. A perturbing planet has been shown to 
produce nonaxisymmetric structures, as well as gaps in disks, regardless of the origin of the dust. However, small grains will have very 
different dynamics compared with planetesimals when in the presence of gas, and as such, the collisional evolution of planetesimals could 
create dusty disk structures that would not exist otherwise. In particular, mean motion resonances (MMRs) are extremely nonlinear and could 
drive disk morphologies. We use a direct N-body model to track collision rates in a planetesimal disk under the gravitational influence of an 
external giant planet. We show that a perturbing planet can produce significant variations in the collision rate of planetesimals near the 
MMRs and we explore how the mass and eccentricity of the perturbing planet alters this structure. Finally, we use the CASA image simulator to 
predict what the dust emission sturcture should look like with ALMA and the NG-VLA. Although the dust structure produced by MMRs cannot 
be used to directly measure the properties of the perturbing planet, we show that it can be used to place constraints on its mass and 
eccentricity.
\end{abstract}

@@

Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure in the millimeter wavelength
contiunuum emission. Features such as gaps and asymmetries 
\citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the 
emission provide diagnostics for the physical processes that drive the evolution of the disks. At these wavelengths, much of this light 
is produced by second-generation debris generated through collisional grinding of planetesimals
\citep[see][]{2008ARA&A..46..339W}.

In some cases, these gap features are argued to be an indicator for the presence of a giant planet, either embedded in the disk 
\citep{2015MNRAS.453L..73D} or orbiting externally. An giant perturber can influence the structure of the dust emission in a number 
of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}. Highly 
eccentric perturbers can produce even more complicated structures through secular perturbations \citep{2014MNRAS.443.2541P, 
2015MNRAS.448.3679P}. Mean motion resonances (MMRs) have been shown to open gaps as well
\citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.

Also mention \citet{2020A&A...635A..10S}, looked at dust trapping in resonances with terrestrial SS planets. Also mention 
\citet{2020arXiv200408736G}, detection of a planetesimal collision around Fomalhut.

The dynamics governing the motion of bodies near MMRs is extremely nonlinear, as is determining what the collision rates between 
planetesimals should look like in these regions. For a collection of bodies massive enough to experience the effects of gravitational 
focusing, a large eccentricity dispersion tends to reduce the probability of collision, while enhancements in surface density tends to 
increase it. Due to conservation of the Jacobi energy, MMRs simultaneously enhance the local eccentricity dispersion and also 
enhance the surface density adjacent to the resonance \citep{2000Icar..143...45R, 2017ApJ...850..103B}.

Because the second generation dust production is driven by the planetesimal collision rate, it is crucial to understand how the 
dynamics that drive collisions works. In particular, it is not obvious how to link the readily observable thermal emission from dust in 
protoplanetary disks to the presence of a perturbing giant planet. Due to its nonlinearity, this problem is best studied with N-body 
simulations. Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. So far, studies of 
planetesimal dynamics near MMRs have involved either collisionless test particles \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 
2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.

@@

This work is organized in the following way: In section \ref{sec:dynamics}, we provide an overview of the relevant dynamics that drive 
the evolution of a planetesimal disk under the gravitational influence of an external perturber. We also highlight the shortcomings of secular theory in trying to predict the radial collision rate and motivate the need for N-body simulations with massive, collisional particles. In section \ref{sec:sims} we describe the N-body code that we use and detail the initial conditions that are used for two simulations: one in which the perturber is on a circular orbit and another in which the perturber is given a mildly eccentric orbit. Section \ref{sec:results} presents the results of the two simulations. Next, we generate dust emission maps in section \ref{sec:dust}, under the assumption that collisionally-generated dust will quickly couple with the gas and circularize, and show that radial structure is produced in the vicinity of the MMRs. Using the dust emission maps, section \ref{sec:fitting} explores the feasibility of measuring properties of the perturbing planet from the MMR features in the dust. We then conclude in section \ref{sec:discuss}.

\section{Overview of Relavant Dynamics} \label{sec:dynamics}

@@

@@

\begin{table}
\begin{center}
\caption{Summary of Simulations Run}
\begin{tabular}{lllll} \hline \hline
Name     & Mass of Planet [$M_{jup}$] & Eccentricity of Planet [$e_{jup}$] &  &  \\ \hline
$e_{lo}$ & 1                      & 0.5                            &  &  \\
nom      & 1                      & 1                              &  &  \\
$e_{hi}$ & 1                      & 2                              &  &  \\
$m_{lo}$ & 0.5                    & 1                              &  &  \\
$m_{hi}$ & 2                      & 1                              &  &  \\ \hline
\end{tabular}
\label{tab:sims}
\end{center}
\end{table}

@@

An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
At the beginning of each time step, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.

Add a table describing the parameters of the 5 simulations that are run.

@@

We begin by examining simulations $e_{lo}$, $n$ and $e_{hi}$. The positions of the planetesimals in the x-y plane after 5,000 years of integration is shown in figure \ref{fig:xy}. In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$ and the longitude of perihelion of the planet is shown by the dashed line. Resonances with the perturbing planet are visible via nonaxisymmetric gaps. Upon close inspection of the last few simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A similar substructure reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and \citet{2016ApJ...818..159T} (figure 3). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter mass planet on a circular, coplanar orbit. The presence of these features seems robust to the choice of initial conditions.

The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}. In all cases, the 3:1, 2:1 and 5:3 resonances are readily visible as 'spikes' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$). In the $e_{hi}$ simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these features from the $e_{low}$ simulation can be explained by the fact that the strength of a resonance scales with $e^{q}$ \citep{1994PhyD...77..289M}.

@@

@@

\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 AU, the gaseous component of the solar nebula has a density of $4 \times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 1 mm dust grain with a density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is orders of magnitude smaller than the collision timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.

Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical 
distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth of 0.02 AU to assemble the collision locations into a radial distribution. Most strikingly, the bump that was present near the 2:1 resonance is no longer present in cylindrical distance space, although it suddenly appears again in the $e_{hi}$ simulation. The dip that is present near the 3:1 MMR also disappears and instead presents as a bump in the $e_{hi}$ case. To determine how the resonant bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and between $3.2 < a < 3.35$ AU (near the 2:1 resonance), which is shown by the orange curve. Qualitatively, none of the bump or dip features present are changed by making this exclusion. This suggests that the features near resonance seen in semimajor axis space become 'smeared out' in cylindrical distance space due to the large spread in eccentricity and orbital orientation.

This also suggests that the features seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance. To further understand this, we revisit the nonaxisymmetric structure seen in figure \ref{fig:xy}. In figure \ref{fig:coll_polar_e}, we compare the radial collision profile to the polar structure seen in the $e_{low}$, $n$ and $e_{hi}$ simulations. In the lowest forced eccentricity case, the pileups near the edges of the resonances line up with the boundaries of the dip feature seen in the radial collision profile. This is especially prominent for the 2:1 resonance. As discussed previously, the pileups and gaps seen in polar coordinates follow the position of the giant planet in its orbit.

@@

@@

Orange curves in figure \ref{fig:coll_polar_e} show the simulated ALMA flux profiles generated with {\sc CASA} \citep{2007ASPC..376..127M}. Have Aaron add in some more text here describing exactly how the profiles were created.

@@

We show the polar structure of the $m_{low}$, $n$ and $m_{hi}$ simulations in figure \ref{fig:coll_polar_m} alongside the radial collision profile. In all three cases, the eccentricity of the perturbing planet is set to $e_{jup}$. Changes in the apocenter and pericenter distances of the edges of the resonances are entirely due to changes in the libration width here. For the $m_{low}$ and $n$ simulations, the inner apocenter and outer pericenter distances near the 2:1 MMR are quite similar and no strong features appear in the collision profile near this region. For the $m_{hi}$ case, the edges of the resonances are sufficiently far apart to allow a gap near the center of the 2:1 resonance to appear in the collision profile.

\section{Constraining the Mass and Eccentricity of the Planet}

@@

\section{Summary and Conclusions}

In this work, we have shown that mean-motion resonances with a perturbing planet produce significant variations in the collision rate of a planetesimal disk. In contrast to \citet{2000Icar..143...45R}, we find that the more prominent interior MMRs, including the 2:1, 3:1 and 5:3, all produce structures in the collision profile as a function of semimajor axis. Furthermore, we found a series of distinctly different features that appear when collisions are grouped by cylindrical distance from the central star. If enough gas from the protoplanetary disk is still present, dust generated from planetesimals collisions will immediately couple to it and fall onto a circular orbit. In this case, variations in the radial collision profile will match the radial dust emission profile, which can potentially be observed in the sub-mm.

Near the interior 2:1 MMR, we find that a distinct bump or dip feature is generated in the dust profile. The presence of either of these structures can used to constrain the mass and eccentricity of the perturbing planet. For a high mass, low eccentricity planet, a dip will form in the dust profile because the edges of the resonance, where many collisions occur, stay sufficiently separated. If the planet has a low enough mass (which shrinks the size of the resonance) or is sufficiently eccentric (which decreases the separation between the apocenter and pericenter distances of the inner and outer edges of the resonance), a bump will instead form. We tested this hypothesis for five different combinations of the planet's mass and eccentricity and found that this diagnostic is useful as long as the planet is sufficiently far from the dividing line in parameter space. This diagnostic is more clear for massive, eccentric planets, because the strength of the resonant perturbations scale linearly with both of these quantities.

The results presented here appear to be broadly consistent with \citet{2016ApJ...818..159T}, which used collisionless, massless test particles to model a planetesimal disk perturbed by a planet. In their case, a dip feature appeared in the azimuthally averaged surface density profile was seen, although they did use a high enough eccentricity planet in any of their simulations to produce a bump. Another thing to note is that the gap morphology seen by \citet{2016ApJ...818..159T} was markedly different for the 2:1 exterior MMR. Whether this would alter the radial collision profile for the exterior, rather then the interior 2:1 resonance, is not immediately clear.  Given that the solid surface density diminishes with distance ($\sim r^{3/2}$ for the MMSN \citep{1981PThPS..70...35H}), exterior resonances may not be quite as useful for this type of measurement.

Our conclusion that the bodies in resonance do not significantly contribute to the radial collision profile (see figure \ref{fig:coll_hist_a}) does appear support the simplifying assumptions made by \citet{2017ApJ...850..103B}, in which dynamically cold, low eccentricity regions of test particles were assumed to trace the regions of second-generation dust production. Besides the corotation regions, nonaxisymmetric structure near resonances does not appear to be present in \citet{2017ApJ...850..103B}. This makes it difficult to determine whether a simpler model in which test particles 'trace' the collision rate can be used to generate a dust profile.

Resolving these structures is really pushing the capabilities of observatories like ALMA. Mention NG-VLA. Also {\sc Frankenstein} \citep{2020arXiv200507709J}.

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/xy.png}
    \caption{Non axisymmetric gaps and rings appear near MMRs. More features appear at higher eccentricities. Gap features
    at $\theta$ = 0 and $\theta = \pi$ follow the giant planet in its orbit. (Update this to show long of peri of Jupiter)\label{fig:xy}}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/ae.png}
    \caption{The MMRs produce spikes in the a-e plane. Between resonances, the nonzero eccentricity is caused by secular
    forcing by the planet. At larger eccentricities, the higher order resonances become more prominent because of the steeper
    scaling with $e$.\label{fig:ae}}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/long_ph.png}
    \caption{The MMRs also induce precession which overpowers the secular forcing. Inside of the resonances, orbits of
    planetesimals are effectively randomized.\label{fig:long_ph}}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/coll_hist_a.png}
    \caption{In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision
    rate decreases, while it gets enhanced near the 2:1. This is because gravitational focusing is already suppressed
    near the 2:1. Additional heating by the resonance increases the encounter rate.\label{fig:coll_hist_a}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/coll_hist_r.png}
    \caption{The features near resonance that appear in cylindrical distance space appear qualitatively different.
    The orange curve shows collisions with bodies inside the 2:1 and 3:1 MMR excluded. This does not qualitatively
    change any of the plots, and we infer that the features seen here are produced by bodies outside of resonance.
    Most interestingly,  the highest eccentricity planet simulation produces bumps, rather than dips near the 2:1 and
    3:1 MMR.\label{fig:coll_hist_r}}
\end{center}
\end{figure}

>>>>

\documentclass[twocolumn]{aastex63}
\usepackage{natbib}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
\bibliographystyle{aasjournal}

@@

\begin{abstract}
In circumstellar disks, collisional grinding of planetesimals produces second-generation dust which can be observed through thermal 
emission. While it remains unclear when second-generation dust first becomes a major component of the total dust content, the presence of 
such dust and potentially the substructure within it can be used to explore a disk's physical conditions. A perturbing planet has been shown to 
produce nonaxisymmetric structures, as well as gaps in disks, regardless of the origin of the dust. However, small grains will have very 
different dynamics compared with planetesimals when in the presence of gas, and as such, the collisional evolution of planetesimals could 
create dusty disk structures that would not exist otherwise. Previous studies have shown that morphological differences in the collisional dust 
corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small. Going further, we investigate the 
production of second-generation dust near prominent mean-motion resonances with the planet using N-body simulations that directly resolve 
collisions between planetesimals. We find that a distinct over- or under-density in the dust emission is produced at the interior 2:1 mean motion 
resonance, depending on the mass and eccentricity of the planet. The presence of one of these two features can be used to place simultaneous 
upper or lower limits on the mass and eccentricity of the perturbing body.
\end{abstract}

@@

Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure in the millimeter contiunuum emission. Features 
such as gaps and asymmetries 
\citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide 
diagnostics for the physical processes that drive the evolution of the disks. In some cases, these gap features are argued to be an indicator for the 
presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally. A giant perturber can influence the 
structure of the continuum emission in a number of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps 
\citep{2001A&A...370..447A}. Highly eccentric perturbers can produce even more complicated structures through secular perturbations 
\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}. Mean motion resonances (MMRs) have been shown to open gaps as well 
\citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.

Collisions between planetesimals are thought to be a significant source of dust for many young circumstellar disks 
\citep[see][]{2008ARA&A..46..339W}. An expanding debris cloud from a planetesimal collision was recently detected through scattered light in the 
Fomalhut system \citep{2020PNAS..117.9712G}. Although some amount of primordial dust is likely still present during the planet formation process, 
ongoing collisions between small bodies will augment this and could be used to trace the underlying dynamical activity of the planetesimals. 
\citet{2013ApJ...777L..31D} showed that collisional dust generated near the gap formed by a giant planet in a planetesimal disk should produce a 
distinctly observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological differences in 
the dust emission could be used to distinguish between a low and high eccentricity planet \citep{2016ApJ...820...29D}.

Although more difficult to spatially resolve, substructure due to mean-motion resonances (MMRs) with a giant planet may hold additional clues which 
could be used to constrain the properties of the planet.  The width of a resonance is set by both the mass of the perturbing planet, along with the 
unperturbed eccentricity of the planetesimals, which is in turn set by the eccentricity of the planet through secular forcing. Therefore, the structure of 
second generation dust produced near MMRs may hold information about both the mass and eccentricity of the planet.

The dynamics governing the motion of bodies near MMRs is extremely nonlinear, as is determining what the collision rates between planetesimals 
should look like in these regions. For a collection of bodies massive enough to experience the effects of gravitational focusing, a large eccentricity 
dispersion tends to reduce the probability of collision, while enhancements in surface density tends to increase it. Due to conservation of the Jacobi 
energy, MMRs simultaneously enhance the local eccentricity dispersion and also enhance the surface density adjacent to the resonance 
\citep{2000Icar..143...45R, 2017ApJ...850..103B}. Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. 
So far, studies of planetesimal dynamics near MMRs have involved either collisionless test particles 
\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.

@@

This work is organized in the following way: In section \ref{sec:dynamics}, we provide an overview of the relevant dynamics that drive the evolution 
of a planetesimal disk under the gravitational influence of an external perturber. In section \ref{sec:sims} we provide an overview of the N-body code 
that we use and describe the initial conditions that are used for five simulations in which a perturbing giant planet is given is given various masses 
and eccentricities. Section \ref{sec:results} presents the results of these five simulations and we use the collision statistics to generate synthetic dust 
emission profiles that would be detected with observing facilities like ALMA. Next, we show in section \ref{sec:constrain} that a characteristic bump 
or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
planet. We discuss the potential of using this feature to place and upper or lower on the mass and eccentricity of the planet and conclude in section 
\ref{sec:conclusions}.

\section{Overview of Relevant Dynamics} \label{sec:dynamics}

@@

\begin{table}
\begin{center}
\caption{Summary of Simulations Run}
\begin{tabular}{lllll} \hline \hline
Name     & Mass of Planet & Eccentricity of Planet &  &  \\ \hline
e1m2 & 1.0 $M_{jup}$                     & 0.5 $e_{jup}$                            &  &  \\
e2m2      & 1.0 $M_{jup}$                     & 1.0 $e_{jup}$                             &  &  \\
e3m2 & 1.0 $M_{jup}$                     & 2.0 $e_{jup}$                             &  &  \\
e2m1 & 0.5 $M_{jup}$                   & 1.0 $e_{jup}$                             &  &  \\
e2m3 & 2.0 $M_{jup}$                     & 1.0 $e_{jup}$                             &  &  \\ \hline
\end{tabular}
\label{tab:sims}
\end{center}
\end{table}

@@

@@

An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
To start, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/xy.png}
    \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
    indicates the position of the giant planet and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
    are apparent near the locations of MMRs. At higher eccentricities, more resonances become visible. At the 2:1 MMR, gap features at $\theta$ = 0 
    and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/ae.png}
    \caption{The semimajor axes and eccentricities of the remaining planetesimals are shown, with the locations of prominent resonances indicated 
    by the vertical dashed lines. Libration of the critical angle drives large variations in eccentricity, which produce spikes in the a-e plane. Between 
    the resonances, the nonzero eccentricity is due to secular forcing by the planet.\label{fig:ae}}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/long_ph.png}
    \caption{Shown here are the longitudes of pericenter and semimajor axes of the remaining planetesimals. The dashed lines again indicate the 
    locations of prominent MMRs. Close to the resonances, the critical angle librates and drives fast precession of the longitudes of pericenter of the 
    bodies. This overpowers the secular forcing by the planet and effectively randomizes the orientations of their orbits.\label{fig:long_ph}}
\end{center}
\end{figure*}

@@

We begin by examining simulations e1m2, e2m2 and e3m2. The positions of the planetesimals in the x-y plane after 5,000 years of integration is 
shown in figure \ref{fig:xy}. In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$ and the longitude of perihelion of 
the planet is shown by the dashed line. Resonances with the perturbing planet are visible via nonaxisymmetric gaps. Upon close inspection of the 
last few simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A 
similar substructure reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and \citet{2016ApJ...818..159T} (figure 3). It is worth 
noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter mass planet on a circular, coplanar orbit. The 
presence of these features seems robust to the choice of initial conditions.

The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}. In all cases, 
the 3:1, 2:1 and 5:3 resonances are readily visible as 'spikes' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$). In the 
e3m2 simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these features from the e1m2 simulation can be 
explained by the fact that the strength of a resonance scales with $e^{q}$ \citep{1994PhyD...77..289M}.

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/coll_hist_a.png}
    \caption{In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision
    rate decreases from its unperturbed value, while an enhancement apepars near the 2:1.\label{fig:coll_hist_a}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/coll_hist_r.png}
    \caption{Here, collisions are instead ordered by cylindrical distance from the star. Features near the 3:1 and 2:1 MMRs are still present, but appear qualitatively different than in semimajor axis space. At low eccentricities, a dip appears around the center of the resonance. At the highest eccentricity, a bump is formed instead. In orange, the collision profile is shown with collisions between bodies in resonance removed. The bump and dip features remain qualitatively the same, which suggests that they are produced by bodies outside of resonance.\label{fig:coll_hist_r}}
\end{center}
\end{figure}

@@

\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $
\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 AU, the gaseous component of the solar nebula has a density of $4 
\times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 1 mm dust grain with a 
density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is orders of magnitude smaller than the 
collision timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.

Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical 
distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth 
of 0.02 AU to assemble the collision locations into a radial distribution. Most strikingly, the bump that was present near the 2:1 resonance is no 
longer present in cylindrical distance space, although it suddenly appears again in the e3m2 simulation. The dip that is present near the 3:1 MMR 
also disappears and instead presents as a bump in the e3m2 case. To determine how the resonant bodies actually contribute to the radial collision 
profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and between $3.2 < a < 3.35$ AU (near the 2:1 
resonance), which is shown by the orange curve. Qualitatively, none of the bump or dip features present are changed by making this exclusion. This 
suggests that the features near resonance seen in semimajor axis space become 'smeared out' in cylindrical distance space due to the large spread 
in eccentricity and orbital orientation.

This also suggests that the features seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance. To further understand this, 
we revisit the nonaxisymmetric structure seen in figure \ref{fig:xy}. In figure \ref{fig:coll_polar_e}, we compare the radial collision profile to the polar 
structure seen in the e1m2, e2m2 and e3m2 simulations. In the lowest forced eccentricity case, the pileups near the edges of the resonances line up 
with the boundaries of the dip feature seen in the radial collision profile. The locations of the edges of the resonances are calculated using equations 
\ref{eq:res_fo} and \ref{eq:res_so}. The pileups are especially prominent for the 2:1 resonance. As discussed previously, the pileups and gaps seen 
in polar coordinates follow the position of the giant planet in its orbit.

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/coll_polar_e.png}
    \caption{The collision profiles in figure \ref{fig:coll_hist_r} are shown alongside the positions of the planetesimals, in polar coordinates. The 
    synthetic dust emission profiles are shown in orange. The dashed and solid lines show the pericenter and apocenter of bodies at the edge of the 
    3:1 and 2:1 MMR. In these figures, the longitude of pericenter of the planet lies at $\theta = 0$ and the present position of the planet is indicated 
    by the vertical line. For the 2:1 resonance, a bump, rather than a dip feature appears when the inner edge or the resonance's apocenter and outer 
    edge's pericenter distance cross. The collision profile near the 3:1 resonance does not appear to follow this same qualitative behavior.
    \label{fig:coll_polar_e}}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/coll_polar_m.png}
    \caption{Similar to figure \ref{fig:coll_polar_e}, except the eccentricity of the planet is kept constant and the mass is varied.
    This has the effect of changing the width of the resonances, without altering the relative apo or peri distances of
    bodies near the edges. Except for the highest mass case, the apocenter and pericenter distances of the inner and outer edges of the 2:1 
    resonance are too close together to produce much of a dip or a bump feature.\label{fig:coll_polar_m}}
\end{figure*}

@@

Orange curves in figure \ref{fig:coll_polar_e} show the simulated ALMA flux profiles generated with {\sc CASA} \citep{2007ASPC..376..127M}. Have 
Aaron add in some more text here describing exactly how the profiles were created. Should we add a separate figure to show the flux profiles, or 
include them in figures 6 and 7 like I've started to do here?

@@

We show the polar structure of the e2m1, e2m2 and e2m3 simulations in figure \ref{fig:coll_polar_m} alongside the radial collision profile. In all three 
cases, the eccentricity of the perturbing planet is set to $e_{jup}$. Changes in the apocenter and pericenter distances of the edges of the 
resonances are entirely due to changes in the libration width here. For the e2m1 and e2m2 simulations, the inner apocenter and outer pericenter 
distances near the 2:1 MMR are quite similar and no strong features appear in the collision profile near this region. For the e2m3 case, the edges of 
the resonances are sufficiently far apart to allow a gap near the center of the 2:1 resonance to appear in the collision profile.

\section{Constraining the Mass and Eccentricity of the Planet}\label{sec:constrain}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/bump_dip_diag.png}
    \caption{The presence of a dip or bump near the resonances can be used to constrain the mass and eccentricity
    of the perturbing planet. The color scale indicates the relative strength of the features, while the dashed lines
    indicate boundaries in parameter space where a dip or a bump will be produced at the resonance. Combinations of mass and eccentricity that fall 
    between the dashed lines correspond to an inner apocenter and outer pericenter separation at the edges of the resonance that is smaller than the 
    resonance width and therefore will not create any significant feature in the collision profile.\label{fig:bump_dip_diag}}
\end{center}
\end{figure}

@@

\section{Summary and Conclusions}\label{sec:conclusions}

In this work, we have shown that mean-motion resonances with a perturbing planet produce significant local variations in the collision rate of a 
planetesimal disk. In contrast to \citet{2000Icar..143...45R}, we find that the more prominent interior MMRs, including the 2:1, 3:1 and 5:3, all 
produce structure in the collision profile as a function of semimajor axis. Furthermore, we find that a series of distinctly different features appear 
when collisions are sorted by cylindrical distance from the central star. If enough gas from the protoplanetary disk is still present, dust generated 
from planetesimals collisions will immediately couple to it and fall onto a circular orbit. In this case, the radial dust emission profile, which can be 
observed in the sub-mm, directly traces the radial collision rate and therefore the dynamical activity of the planetesimals.

Near the interior 2:1 MMR, we find that a distinct bump or dip feature is generated in the dust profile. The presence of one of these two structures 
can used to constrain the mass and eccentricity of the perturbing planet. For a high mass, low eccentricity planet, a dip will form in the dust profile 
because the edges of the resonance, where many collisions occur, stay sufficiently separated. If the planet has a low enough mass (which shrinks 
the size of the resonance) or is sufficiently eccentric (which decreases the separation between the apocenter and pericenter distances of the edges 
of the resonance), a bump will instead form. We tested this hypothesis for five different combinations of the planet's mass and eccentricity and found 
that a distinct bump or dip signature is produced as long as the planet properties are sufficiently far from the dividing line in parameter space. This 
diagnostic is more useful for massive, eccentric planets, because the strength of the resonant perturbations scale linearly with both of these 
quantities.

The results presented here appear to be broadly consistent with \citet{2016ApJ...818..159T}, which used collisionless, massless test particles to 
model a planetesimal disk perturbed by a planet. In their case, a dip feature can be seen in the azimuthally averaged surface density profile, 
although they did not test a high enough eccentricity planet in any of their simulations to produce a bump. Another thing to note is that the gap 
morphology seen by \citet{2016ApJ...818..159T} was markedly different for the 2:1 exterior MMR. Whether this would alter the radial collision profile 
for the exterior, rather than the interior 2:1 resonance, is not immediately clear.  Given that the solid surface density diminishes with distance 
($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), exterior resonances may not be quite as useful for this type of measurement.

Compared to using the gap around the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring variations in the dust 
emission near higher order MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the bump vs 
dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary disks. Another complicating factor is that the inner 
$\sim$ 10 AU of most protoplanetary disks are optically thick in the sub-mm. The solution to this problem is to instead observe in the radio, which 
achieves much poorer resolution. However, future radio facilities like the NG-VLA are expected to achieve sub-AU resolution for nearby planet-
forming disks \citep{2018ASPC..517..147R}. In the more near-term, techniques like Gaussian process fitting present a promising way to recover 
substructure at sub-beam resolution \citep{2020arXiv200507709J}.
